Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-23 paper/ICPC19/icpc19.tex
RQs draft

\begin{framed}
\textit{\textbf{RQ1} What is the impact of fixing vulnerabilities to improve security }
\end{framed}

>>>>

\begin{framed}
\textit{\textbf{RQ1} What is the impact of security refactorings on the maintainability of open-source software?}
\end{framed}

\begin{framed}
\textit{\textbf{RQ2} Which patterns of security refactorings are more likely to affect open-source software maintainability?}
\end{framed}

\begin{framed}
\textit{\textbf{RQ3} }
\end{framed}
